\bf Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-04-16 doc/paper.Rmd
explanation of histograms

In a pre-processing step  the two markings are smoothed using a lowess \citep{lowess} with coarseness parameter $c$. 
 Originally, this smoothing is intended to remove drift and (sub)class characteristics from individual markings, however, in the setting of matching bullet striae, we can also make use of this mechanism can be used to separate bullet curvature in profiles from signatures before matching signatures.

@@

\hh{XXX We have been operating under a false assumption: smoothing the signature at f=1 DOES change it - see figure \ref{fig:profile-sketch}. We need to re-run some of the results to compare the results against a }

```{r profile-sketch, fig.height = 5, fig.width='\\textwidth', fig.cap="Overview of the effect of different coarseness parameters $c$ on the profile shown in Figure \\ref{fig:sigs-profiles}. "}
profile <- sigs_graphics[[1]] %>% filter(land_id==19)
profile$lw20 <- lowess(x = profile$y, y = profile$value, f=.20)$y
profile$lw25 <- lowess(x = profile$y, y = profile$value, f=.25)$y
profile$lw30 <- lowess(x = profile$y, y = profile$value, f=.30)$y
#profile$lw50 <- lowess(x = profile$y, y = profile$value, f=.5)$y
#profile$lw75 <- lowess(x = profile$y, y = profile$value, f=.75)$y
#profile$lw100 <- lowess(x = profile$y, y = profile$value, f=1)$y

@@

profc20 <- readRDS("../data/profiles-coarseness/chumbley-csafe-profiles-inv-wo_160-wv_30-c_20.rds")
profc20$coarseness <- 0.2
profc25 <- readRDS("../data/profiles-coarseness/chumbley-csafe-profiles-inv-wo_160-wv_30-c_25.rds")
profc30 <- readRDS("../data/profiles-coarseness/chumbley-csafe-profiles-inv-wo_160-wv_30.rds")
profc30$coarseness <- .30
profc <- bind_rows(profc20, profc25, profc30)
profc <- profc %>% mutate(
  locations = chumbley %>% purrr::map_int(.f = function(x) {
    res <- NULL
    try(res <- x$locations[1], silent = TRUE)
    res
  })
)
# profsumm <- read.csv("../data/profiles-summary.csv")
# profsumm <- profsumm %>% select(-run_id)
# profc <- profc %>% left_join(profsumm, by=c("land2_id"="land_id", "profile2_id"="profile_id"))
# 
# p2 <- profc %>% 
#   ggplot(aes(x = locations/(length-wo))) +
#   geom_histogram(binwidth = 0.025) +
#   facet_grid(.~coarseness, labeller="label_both") + 
#   theme_bw()
#  
# grid.arrange(p1, p2, ncol=1)
```

\hh{Figure \ref{fig:coarse} shows the type II error rates for profiles using an optimization window $w_o= 120$ and a validation window $w_v = 30$ for varying level of coarseness. The type II error for all nominal levels of  $\alpha$ are the lowest for a coarseness range of 0.20 to 0.35. For the remainder of the analysis we use a fixed value of coarseness of 0.25. }

>>>>

In a pre-processing step  the two markings are smoothed using a lowess \citep{lowess} with coarseness parameter $c$. 
 Originally, this smoothing is intended to remove drift and (sub)class characteristics from individual markings, however, in the setting of matching bullet striae, we can also make use of this mechanism to separate bullet curvature in profiles from signatures before matching signatures.

@@

\hh{\autoref{fig:profile-sketch} gives an overview of the effect of different coarseness parameters: from left to right, coarseness levels $c$ are 0.2, 0.25, and 0.3, respectively. The top row shows the resulting signature after smoothing the profile shown in Figure~\ref{fig:sigs-profiles} with the coarseness specified. The histograms in the bottom row show the relative optimal location $t^o$ (optimal location $t^o$ divided by the length of the corresponding profile). Optimal locations should be distributed uniformly. However, for coarseness values of $c = 0.25$ and $c=0.30$ we see very distinct boundary effects: optimal locations $t^o$ are found at the very extreme ends of a profile more often than one would expect based on a uniform location.}

```{r profile-sketch, fig.height = 5, fig.width='\\textwidth', fig.cap="Overview of the effect of different coarseness parameters $c$ on the profile shown in Figure \\ref{fig:sigs-profiles} (top). The bottom row shows histograms of  the (relative) optimal locations $t^o$ identified in the optimization step for different values of the coarseness parameter $c$. "}
profile <- sigs_graphics[[1]] %>% filter(land_id==19)
profile$lw20 <- lowess(x = profile$y, y = profile$value, f=.20)$y
profile$lw25 <- lowess(x = profile$y, y = profile$value, f=.25)$y
profile$lw30 <- lowess(x = profile$y, y = profile$value, f=.30)$y
#profile$lw50 <- lowess(x = profile$y, y = profile$value, f=.5)$y
#profile$lw75 <- lowess(x = profile$y, y = profile$value, f=.75)$y
#profile$lw100 <- lowess(x = profile$y, y = profile$value, f=1)$y

@@

profc20 <- readRDS("../data/profiles-coarseness/chumbley-csafe-profiles-inv-wo_160-wv_30-c_20.rds")
profc20$coarseness <- 0.2
profc25 <- readRDS("../data/profiles-coarseness/chumbley-csafe-profiles-inv-wo_160-wv_30-c_25.rds")
profc30 <- readRDS("../data/profiles-coarseness/chumbley-csafe-profiles-inv-wo_160-wv_30.rds")
profc30$coarseness <- .30
profc <- bind_rows(profc20, profc25, profc30)
profc <- profc %>% mutate(
  locations = chumbley %>% purrr::map_int(.f = function(x) {
    res <- NULL
    try(res <- x$locations[1], silent = TRUE)
    res
  })
)

profsumm <- read.csv("../data/profiles-summary.csv")
profsumm <- profsumm %>% select(-run_id)
profc <- profc %>% left_join(profsumm, by=c("land2_id"="land_id", "profile2_id"="profile_id"))

p2 <- profc %>% 
  ggplot(aes(x = locations/(length-wo))) +
  geom_histogram(binwidth = 0.025) +
  facet_grid(.~coarseness, labeller="label_both") + 
  theme_bw() +
  xlab(expression("Relative optimal location "~t^o)) +
  ylab("Number of profiles")

grid.arrange(p1, p2, ncol=1)
```

\hh{Figure \ref{fig:coarse} shows the type II error rates for profiles using an optimization window $w_o= 120$ and a validation window $w_v = 30$ for varying level of coarseness. The type II error for all nominal levels of  $\alpha$ are the lowest for a coarseness range of 0.20 to 0.30. For the remainder of the analysis we use a fixed value of coarseness of 0.25. }

### 2018-04-16 doc/paper.tex
explanation of histograms

In a pre-processing step the two markings are smoothed using a lowess
\citep{lowess} with coarseness parameter \(c\). Originally, this
smoothing is intended to remove drift and (sub)class characteristics
from individual markings, however, in the setting of matching bullet
striae, we can also make use of this mechanism can be used to separate
bullet curvature in profiles from signatures before matching signatures.

@@

\hh{XXX We have been operating under a false assumption: smoothing the signature at f=1 DOES change it - see figure \ref{fig:profile-sketch}. We need to re-run some of the results to compare the results against a }

@@

\caption{Overview of the effect of different coarseness parameters $c$ on the profile shown in Figure \ref{fig:sigs-profiles}. }\label{fig:profile-sketch}
\end{figure}

\hh{Figure \ref{fig:coarse} shows the type II error rates for profiles using an optimization window $w_o= 120$ and a validation window $w_v = 30$ for varying level of coarseness. The type II error for all nominal levels of  $\alpha$ are the lowest for a coarseness range of 0.20 to 0.35. For the remainder of the analysis we use a fixed value of coarseness of 0.25. }

>>>>

In a pre-processing step the two markings are smoothed using a lowess
\citep{lowess} with coarseness parameter \(c\). Originally, this
smoothing is intended to remove drift and (sub)class characteristics
from individual markings, however, in the setting of matching bullet
striae, we can also make use of this mechanism to separate bullet
curvature in profiles from signatures before matching signatures.

@@

\hh{XXX We have been operating under a false assumption: smoothing the signature at f=1 DOES change it - see figure \ref{fig:profile-sketch}. We need to re-run some of the results }

@@

\caption{Overview of the effect of different coarseness parameters $c$ on the profile shown in Figure \ref{fig:sigs-profiles} (top). The bottom row shows histograms of  the optimal locations $t^o$ identified in the optimization step for different values of the coarseness parameter $c$. }\label{fig:profile-sketch}
\end{figure}

\hh{Figure \ref{fig:coarse} shows the type II error rates for profiles using an optimization window $w_o= 120$ and a validation window $w_v = 30$ for varying level of coarseness. The type II error for all nominal levels of  $\alpha$ are the lowest for a coarseness range of 0.20 to 0.30. For the remainder of the analysis we use a fixed value of coarseness of 0.25. }
